Fail Faster

### 2025-03-19 paper/paper.tex
other langs and libs

\jwc{Note that this explanation require some prior note of exactly *why* BQ is slow... i.e. the abstraction overhead of the library is high.}

\jwc{
  \begin{itemize}
    \item Python. Maybe could do it?? Hypothesis + MacroPy
    \item Haskell: GHC does a lot of these optimizations already, since the code is pure. Since QC generators are relatively small programs,
    GHC has little trouble specializing them. Of course, this is not guaranteed. A version of this idea can easily be ported to the original QC with template haskell, to guarantee
    the highest-performance generators.
    \item Rust: Not GC'd, so no alloc overhead but bind'd generators still dispatch through run-time data.
  \end{itemize}
}

>>>>

In the years since the original QuickCheck paper \cn{}, PBT has had remarkable success
in languages outside of

Of course, users and developers of PBT libraries in \emph{other} languages might be curious about how
the techniques brought to bear on OCaml's \bq{} and Scala's ScalaCheck in this paper might be imported to their favorite language.

Indeed, while we have done our best to keep the proceeding discussion as
language-agnostic as possible, our claims about the \name{} technique have only
been thoroughly tested in OCaml and Scala 3, and we are only claiming (in the
scientific sense) that we have contributed a technique applicable to PBT
libraries in strict functional programming languages.

In this section

\jwc{
  \begin{itemize}
    \item Racket is the only ``real'' strict functional language we haven't tested this in. It'd definitely work.
    \item Haskell GHC does a lot of these optimizations already, since the code is pure. Since QC generators are relatively small programs,
    GHC has little trouble specializing them. Of course, this is not guaranteed. A version of this idea can easily be ported to the original QC with template haskell, to guarantee
    the highest-performance generators. But the benefit would be lower since GHC is smarter. Worth doing, though.
    \item Rust: generator libraries are not monadic, presumably to avoid exactly these issues.
    \item Python. Maybe could do it?? Hypothesis is the most used PBT library out there so this could be high impact.
  \end{itemize}
}
